Pillar 1 - Sequential Pattern Mining

### 2019-02-13 Pillar 1 - Sequential Pattern Mining.Rmd
SR conf & lift by hand

@@

### not take -> fail
```{r}

@@

### grade less than or equal to x -> grade less than or equal to 6
```{r}
SR$G <- sequences$G %>%

@@

# Remove objects
rm(
  my_cspade, my_ruleInduction, clean_rules, compute_rhs.support, edit_rules, make_SR,
  SR, sequences
)
```

```{r SR metrics}
    # Compute statistic
    group_by(lhs,`RHS Course ID`) %>%
    mutate(
      lhs.rhsCourse.support = sum(support),
      confidence = case_when(is.na(`RHS Quality`) ~ confidence,
                             T ~ (support / lhs.rhsCourse.support)),
      count = support * n_students,
      lhs.rhsCourse.count = lhs.rhsCourse.support * n_students,
      lift = 1 #dummy variable
      # TODO: compute rhs.support
      # lift = confidence.corr / rhs.support
     ) %>%
    ungroup() %>%
```

SR_TPF are manually computed
```{r}
# current, past, not_yet
SR_TPF <- d_transcript_cum                         %>%
  select(sequenceID, eventID, course_current, course_not_so_far)    %>%
  unnest(course_current, .drop = F)                %>%
  unnest(course_not_so_far)                        %>%
  left_join(
    select(d_transactions$TPF, 
           sequenceID, eventID, item, PF), 
    by= c("sequenceID" = "sequenceID", "eventID" = "eventID", "course_current" = "item")
    )                                              %>%
  select(sequenceID,eventID, course_not_so_far, course_current, PF) %>%
  rename(
    lhs="course_not_so_far", 
    rhs.x = "course_current", 
    rhs.PF = "PF")                                 %>%
  mutate(num_transactions = n())                   %>%
  group_by(lhs)                                    %>%
  mutate(
    num_lhs = n(),
    support_lhs         = num_lhs / num_transactions
    )                                              %>%
  group_by(rhs.x)                                  %>%
  mutate(
    num_rhs.x           = n(),
    support_rhs.x       = num_rhs.x / num_transactions
         )                                         %>%
  group_by(rhs.x,rhs.PF)                           %>%
  mutate(
    num_rhs.PF          = n(),
    support_rhs.PF      = num_rhs.PF / num_transactions
  )                                                %>%
  group_by(lhs, rhs.x)                             %>%
  mutate(
    num_rule_x          = n(),
    support_rule_rhs.x  = num_rule_x / num_transactions
  )                                                %>%
  group_by(lhs, rhs.x, rhs.PF)                     %>%
  mutate(
    num_rule_PF          = n(),
    support_rule_rhs.PF  = num_rule_PF / num_transactions,
    support_rhs_bounded  = num_rule_PF / num_rule_x
         )                                         %>%
  ungroup()                                        %>%
  mutate(
    confidence                   = support_rule_rhs.PF / support_lhs,
    confidence_bounded           = support_rhs_bounded / support_lhs, #not sure about this 
    lift                         = confidence / support_rhs.PF,
    lift_bounded                 = confidence_bounded /support_rhs_bounded #not sure about this
  )
```

>>>>

  # Confidenca and lift by hand
  group_by(
    lhs,
    rhs_course
    ) %>%
  mutate(
    lhs.rhsTake.support = sum(support), # Proba of (lhs => taking rhs course)
    lhs.rhsTake.count   = lhs.rhsTake.support * n_students
  ) %>%
  ungroup %>%

  mutate(
    confidence = support / lhs.rateTake.support,
    lift       = confidence / rhs.support
    )

@@

### not take -> fail
```{r, eval = FALSE}

@@

### grade less than or equal to x -> grade less than or equal to 6
```{r, eval = FALSE}
SR$G <- sequences$G %>%

@@

# Remove objects
rm(
  SR, sequences,
  my_cspade, my_ruleInduction, clean_rules, compute_rhs.support, edit_rules, make_SR,
  n_students
)
```

SR_TPF are manually computed
```{r, eval = FALSE}
# current, past, not_yet
SR_TPF <- d_transcript_cum                         %>%
  select(sequenceID, eventID, course_current, course_not_so_far)    %>%
  unnest(course_current, .drop = F)                %>%
  unnest(course_not_so_far)                        %>%
  left_join(
    select(d_transactions$TPF, 
           sequenceID, eventID, item, PF), 
    by= c("sequenceID" = "sequenceID", "eventID" = "eventID", "course_current" = "item")
    )                                              %>%
  select(sequenceID,eventID, course_not_so_far, course_current, PF) %>%
  rename(
    lhs="course_not_so_far", 
    rhs.x = "course_current", 
    rhs.PF = "PF")                                 %>%
  mutate(num_transactions = n())                   %>%
  group_by(lhs)                                    %>%
  mutate(
    num_lhs = n(),
    support_lhs         = num_lhs / num_transactions
    )                                              %>%
  group_by(rhs.x)                                  %>%
  mutate(
    num_rhs.x           = n(),
    support_rhs.x       = num_rhs.x / num_transactions
         )                                         %>%
  group_by(rhs.x,rhs.PF)                           %>%
  mutate(
    num_rhs.PF          = n(),
    support_rhs.PF      = num_rhs.PF / num_transactions
  )                                                %>%
  group_by(lhs, rhs.x)                             %>%
  mutate(
    num_rule_x          = n(),
    support_rule_rhs.x  = num_rule_x / num_transactions
  )                                                %>%
  group_by(lhs, rhs.x, rhs.PF)                     %>%
  mutate(
    num_rule_PF          = n(),
    support_rule_rhs.PF  = num_rule_PF / num_transactions,
    support_rhs_bounded  = num_rule_PF / num_rule_x
         )                                         %>%
  ungroup()                                        %>%
  mutate(
    confidence                   = support_rule_rhs.PF / support_lhs,
    confidence_bounded           = support_rhs_bounded / support_lhs, #not sure about this 
    lift                         = confidence / support_rhs.PF,
    lift_bounded                 = confidence_bounded /support_rhs_bounded #not sure about this
  )
```
